Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
small phrase in full res

Bare in mind that those results were measured on a full resolution triangulation.
Since we compute the curvature of each vertices of the final mesh, a highly triangulated object will
be much slower to process.
We therefore use in practice an adaptive triangulation of the object, refining the mesh
when it is closer from the camera and thus reducing the number of vertices to compute.

>>>>

When computing results using the hierachical algorithm, a higher error can be noted.
This is due to the precomputation of the subdivision that no longer ensures to fetch data
at the center of a mipmap cell. The interpolation done by the GPU reduces the bias but
does not remove it.

Bear also in mind that those results were measured on a full resolution triangulation.
Since we compute the curvature of each vertices of the final mesh, a highly triangulated object will
be much slower to process.
We therefore use in practice an adaptive triangulation of the object, refining the mesh
when it is closer from the camera and thus reducing the number of vertices to compute.
